An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-11 paper.tex

\section*{Introduction}
%
The collection of dynamical data during human walking has a long history
beginning with the first motion pictures and now with modern marker based
motion capture techniques and high fidelity ground reaction load measurements.
Even though years of data on thousands of subjects now exist, this data is not
widely disseminated, well organized, nor available with few or no restrictions.
David Winter's published normative gait data \citep{Winter1990} is widely used
in biomechanical studies, yet it comes from few subjects and only a small
number of gait cycles per subject. This small source has successfully enabled
many other studies, such as powered prosthetic control design \citep{Sup2008}
but success in other research fields using large sets of data for discovery
lead one to believe that more elaborate data sets may benefit the field of
human motion studies. To enable such work, biomechanical data needs to be
shared extensively, organized, and curated to enable future analysts.

@@

Our use case for the data is centered around the need of bio-inspired control
systems for emerging powered prosthetics and orthotics. Ideally, a powered
prosthetic would behave in such a way that the user would feel like their limb
was never disabled. There are a variety of approaches to developing
bio-inspired control systems, some of which aim to mimic the reactions and
motion of an able-bodied person. A modern gait lab is able to collect a variety
of kinematic, kinetic, and physiological data from humans during gait. This
data can potentially be used to drive the design of the human-mimicking
controller. With a rich enough data set, one may be able to identify control
mechanisms used during a human's natural gait and recovery from perturbations.
We have collected data that is richer than previous gait data sets and may be
rich enough for control identification. The data can also be used for
verification purposes for controllers that have been designed in other manners.

>>>>

\section*{Introduction}
%
The collection of dynamical data during human walking has a long history
beginning with the first motion pictures and now with modern marker based
motion capture techniques and high fidelity ground reaction load measurements.
Even though years of data on thousands of subjects now exist, this data is not
widely disseminated, well organized, nor available with few or no restrictions.
David Winter's published normative gait data~\citep{Winter1990} is widely used
in biomechanical studies, yet it comes from few subjects and only a small
number of gait cycles per subject. This small source has successfully enabled
many other studies, such as powered prosthetic control design~\citep{Sup2008}
but success in other research fields using large sets of data for discovery
lead us to believe that more elaborate data sets may benefit the field of
human motion studies. To enable such work, biomechanical data needs to be
shared extensively, organized, and curated to enable future analysts.

@@

But our reasons are not entirely altruistic, as governments and granting
agencies are also encouraging researchers to share data with recent policy
changes. For example, the \cite{EuropeanCommission2012} has outlined publicly
funded data's role in innovation and the \cite{WhiteHouse2013} laid out a plan
for public access to publications and data in 2013. The National Science
Foundation, which partially funds this work, was ahead of the White House and
required all grants to include a data management plan in 2011. This work is a
partial fulfillment of the grant requirements laid out in our grant's data
management plan and we hope that this work can be a good model for
dissemination of biomechanical data.

Our use case for the data is centered around the need for bio-inspired control
systems in emerging powered prosthetics and orthotics. Ideally, a powered
prosthetic would behave in such a way that the user would feel like their limb
was never disabled. There are a variety of approaches to developing
bio-inspired control systems, some of which aim to mimic the reactions and
motion of an able-bodied person. A modern gait lab is able to collect a variety
of kinematic, kinetic, and physiological data from humans during gait. This
data can potentially be used to drive the design of the human-mimicking
controller. With a rich enough data set, one may be able to identify control
mechanisms used during a human's natural gait and recovery from perturbations.
We hypothesize that by forcing the human to recover from external
perturbations, the resulting reactive actions can be used along with system
identification techniques to expose the feedback related relationships among
the human's sensors and actuators. We have collected data that is richer than
previous gait data sets and may be rich enough for control identification. The
data can also be used for verification purposes for controllers that have been
designed in other manners, such as those constructed from first principles
\citep{Geyer2010}.
